Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-08-15 doc/report/msc-report.tex
added 6.1 - results

@@

>>>>

Keywords: Data warehouse, MapReduce, BigTable, Python, distributed

@@

\section{Results}

The goal of this thesis was to build a tool that allows its user to perform
multi-dimensional analysis of a large corpus of data. That goal has been
achieved by implementing a data store that leverages HBase as a backing store
and utilizes the Hadoop MapReduce framework as its import functionality.

The resulting software is a command line application written in Python. The
command line application is the sole interface to the data store. From here the
user can initiate import jobs, start a server for exporting data, and manage
projects folders.

The import jobs are executed on the Hadoop MapReduce framework. The job
execution is delegated to Dumbo, a python module for running Hadoop jobs that
are not written in Java. The job consist of a map function that wraps around the
map function written by the user, and a reducer function that sums together
measurements for each point in the multi-dimensional measurement space. The
output from the MapReduce job is stored in an HBase table.

Data is exported from the data store through an HTTP interface. Queries to the
data store are made with HTTP GET requests. The response is encoded as JSON, a
lightweight computer interchange format. The exports are not parallelized; they
are performed as one or more scans over an HBase table.

The data store is time series based, meaning that all data points are specified
along the time axis, as well as any number of other dimensional axes. A single
level of granularity is used throughout each data set. The values of dimensions
are entirely user-definable.
